A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
Never ending update
Work in progress
Gravitational references update.

Many of the publications with the most influence on our research
~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
propose a cloud-native optimization architecture that features population-based
algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
which planted the seed of thought in our current paper.

@@

We could have used several strategies to evaluate this attraction. Considering
this algorithm takes a similar focus as the study of bacteria growth in
microbiology, where we can observe and analyze the evolution of a population
over time. As in nature' most species, the bigger a specimen is, the more
attractive it is to its mating candidates. To be consistent with both ideas in
our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
to calculate the attraction between two individuals, where we visualize the
individual fitness as its mass when using the equation. In previous work,
Newton's Law of Universal Gravitation has shown success in helping to solve
optimization problems.

>>>>

Many of the publications with the most influence on our research
~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
propose a cloud-native optimization architecture that features population-based
algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
which planted the seed of thought of our current paper.

@@

We could have used several strategies to evaluate this attraction. Considering
this algorithm takes a similar focus as the study of bacteria growth in
microbiology, where we can observe and analyze the evolution of a population
over time. As in nature' most species, the bigger a specimen is, the more
attractive it is to its mating candidates. To be consistent with both ideas in
our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
to calculate the attraction between two individuals, where we visualize the
individual fitness as its mass when using the equation. In previous work,
Newton's Law of Universal Gravitation has shown success in helping to solve
optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
